---
title: "p8105_hw6_al4225"
author: "Anjing"
date: "2022-11-30"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(dplyr)
library(modelr)
knitr::opts_chunk$set(
  fig.width = 7,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2
### Raw data
```{r}
homicide_data = read_csv("./data/homicide-data.csv",
                col_names = TRUE) %>%
  janitor::clean_names() 
homicide_data
```

### Clean and tidy
Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.
```{r}
homicide = 
  homicide_data %>%
  mutate(
    city_state = str_c(city, ", ", state)) %>%
  mutate(disposition_situation = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), "unsolved", "solved"),
         #disposition_situation = as.factor(disposition_situation)
         ) %>%

  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"), 
         victim_race %in% c("White", "Black")) %>%
  mutate(victim_age = as.numeric(victim_age))
homicide
```

### Logistic regression for Baltimore, MD
For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object;
```{r}
Baltimore = 
homicide %>%
  filter(city_state == "Baltimore, MD") %>%
  mutate(
    disposition_situation = ifelse(disposition_situation == "solved", 1, 0),
    victim_race = fct_relevel(victim_race, "White")) %>% 
  select(disposition_situation, victim_age, victim_race, victim_sex)

glm = glm(Baltimore$disposition_situation ~ Baltimore$victim_age + Baltimore$victim_race + Baltimore$victim_sex, 
          family = binomial(link = "logit"))

summary(glm)

```